\bf Visual Inference for Significance and Goodness-of-Fit Testing for a Social Network Model

### 2017-10-30 ASApaper/paper-child.Rnw
couple more mini changes

To explore stochastic actor-oriented models through visual inference, we show a series of lineups to independent observers recruited through Amazon Mechanical Turk. We provide more details on the Turk setup in Section~\ref{sec:res}.

@@

\begin{description}
\item $H_0$: $\beta_k = 0 $
\item $H_A$: $\beta_k \neq 0$
\end{description}

Under the null hypothesis, we assume that the model that generated the network data is the simplest model presented in Section~\ref{sec:models}, model M1. Thus, the five null plots in the lineup are simulations from M1 with $\beta_1, \beta_2$ set to the estimates given in Table~\ref{tab:fittedvalues} for M1. The alternate model is the model with $\beta_1, \beta_2$, and $\beta_k$ in the objective function, with the remaining plot simulated from the appropriate model.

>>>>

A series of these lineups is shown to independent observers recruited through Amazon Mechanical Turk for feedback (more details on the Turk setup in Section~\ref{sec:res}).

@@

\begin{equation}\label{eq:sig}
H_0: \beta_k = 0 \ \ \ \text{ versus } \ \ \ H_A: \beta_k \neq 0
\end{equation}
%\begin{description}
%\item $H_0$: $\beta_k = 0 $
%\item $H_A$: $\beta_k \neq 0$
%\end{description}

Under the null hypothesis, we assume that the model that generated the network data is $M_1$, the simplest model presented in Section~\ref{sec:models}. Thus, the five null plots in the lineup are simulations from M1 with $\beta_1, \beta_2$ set to the estimates given in Table~\ref{tab:fittedvalues} for M1. The alternate model is the model with $\beta_1, \beta_2$, and $\beta_k$ in the objective function, with the remaining plot simulated from the appropriate model.
